### 2017-10-13 Gruba/02-overview.tex

\begin{definition}
\label{def:user}
A user $u = (B_u, R_u, E_u)$ consists of three sets regarding the user's microblogs $B_u$, followers $R_u$ and followees $E_u$, in which each follower/followee per se refers to a user.
\end{definition}

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$.
%
Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower of $b.O$ written as $f$, i.e., $f \in R_{b.O}$, \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ shall \ret{} $b$ or not.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-3ex}
\end{table}
\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

>>>>

\begin{definition}
\label{def:user}
Given a user $u$, $B_u$, $R_u$ and $E_u$ represent her/his microblogs $B_u$, followers $R_u$ and followees $E_u$,  respectively, in which a follower/followee per se refers to a user.
\end{definition}

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$.

Providing a set of users $\mathbb{U}$ and the associated microblogs $\mathbb{B}$, as well as a microblog $b$ and a follower $f$ of its onwer $b.O$, i.e., $f \in R_{b.O}$, system \sys{} builds a \retg{} model for $\mathbb{U}$ and $\mathbb{B}$, upon which 1/0 is returned regarding whether $f$ \ret{s} $b$ or not.

\subsection{\sys{} Framework}
System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
%\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-3ex}
\end{table}
\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
%\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-2ex}
\end{table}
